Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-16 paper_knowledge.tex
Added a reference to Zender's work

\author{
Séverin Lemaignan \and
Raquel Ros \and
E. Akin Sisbot \and
Rachid Alami \and
Michael Beetz
}

\institute{ 
	Séverin Lemaignan \and Raquel Ros \and E. Akin Sisbot \and Rachid Alami
	\at
	CNRS - LAAS, 7 avenue du Colonel Roche, F-31077 Toulouse, France\\
	Université de Toulouse, UPS, INSA, INP, ISAE, LAAS, F-31077 Toulouse, France\\
	\email{\{slemaign, rrosespi, sisbot, rachid\}@laas.fr}
	\and
	Séverin Lemaignan \and Michael Beetz
	\at
	Intelligent Autonomous Systems, Technische Universität München, Munich, Germany\\
	\email{\{lemaigna, beetz\}@in.tum.de}
}

@@

\item \emph{Knowledge representation and management}: the robot is endowed with
an active knowledge base that provides a logically sound symbolic model of its
beliefs of the world, as well as models for each cognitive agent the robot
interacts with. Each of these models is independent and logically consistent,
enabling reasoning on different perspectives of the world that would otherwise
be considered inconsistent (for instance, an object can be visible for the
robot but not for the human. This object can have at the same time the property
\concept{isVisible \textbf{true}} and \concept{isVisible \textbf{false}} using
two different models).  Our platform relies on OWL ontologies (a decidable
subset of the predicate logics) featuring continuous storage, querying and
event triggering over the pool of facts known by the robot.

@@

Dialogue processing in real robots has been explored by several teams.  Brick
and Scheutz~\cite{Brick2007} have contributions regarding natural language
processing in an incremental way, and how this enables instant back-channel
feedback (like nodding). H\"uwel et al.~\cite{Huwel2006} propose the concept of the
\textit{Situated Semantic Unit}: atoms are extracted from sentences, exposing
semantic links to other units. The parser tries to satisfy these links and
rates the semantic interpretation of the sentence. Used in conjunction with
ontologies, their approach offers robustness to ungrammatical or partial
utterances. They validated the approach with an extensive user-study.

@@

Beetz et al.~\cite{Beetz2010} proposes a cognitive architecture called
\textsc{CRAM} (Cognitive Robot Abstract Machine) that integrates
\textsc{KnowRob}~\cite{Tenorth2009a}, a knowledge processing framework based on
Prolog. Its underlying storage is based on an RDF/OWL\footnote{RDF/OWL is a
standard for Description Logics based ontology
(\url{http://www.w3.org/TR/owl2-primer/}).} ontology, derived from
OpenCyc. \textsc{CRAM} and \textsc{KownRob} have been demonstrated on
several real-world scenarios, where natural language recipes extracted from the
Internet had to be translated into plans and executed in a kitchen environment,
perceived and rebuilt on-line by the robots. While Prolog offers more flexible
modeling (no constraints on the arity of predicate, where Description Logics as
used in our work are limited to binary predicates), it is based on the closed
world assumption (if something cannot be inferred to be true, it is inferred to
be false) whereas we rely on the open world assumption, which is more realistic
in real world scenarios. A probabilistic extension of \textsc{KnowRob}, called
\textsc{ProbCog}~\cite{Jain2009} is also available. While in principle
possible, currently the CRAM architecture does not provide explicit support for
interacting with humans.

@@

	\item standard SPARQL\footnote{{\em SPARQL Protocol and RDF Query
	Language}, \url{http://www.w3.org/TR/rdf-sparql-query/}} queries.

@@

\begin{figure}[!ht]
\begin{center}
\scriptsize
\begin{alltt}
>> IMPERATIVE
VP: \textbf{remember} (present simple)
    SUBSENTENCE (aim: that)
      NP: \textbf{I}
      VP: \textbf{want} (present simple)
        direct objects: 
          NP: \textbf{you}
        secondary VP: \textbf{give} ()
              direct objects:
                NP: \textbf{bottle}
              indirect objects:
                NP: \textbf{me}
\end{alltt}
\end{center}
\caption{Raw output of the {\sc Dialogs} parser after processing the
sentence: ``remember that I want you to give me my nice blue bottle.'' 
Nominal groups are not grounded yet.} 
\label{dialog|parser_output}
\end{figure}

>>>>

\author{
S\'everin Lemaignan \and
Raquel Ros \and
E. Akin Sisbot \and
Rachid Alami \and
Michael Beetz
}

\institute{ 
	S\'everin Lemaignan \and Raquel Ros \and E. Akin Sisbot \and Rachid Alami
	\at
	CNRS - LAAS, 7 avenue du Colonel Roche, F-31077 Toulouse, France\\
	Université de Toulouse, UPS, INSA, INP, ISAE, LAAS, F-31077 Toulouse, France\\
	\email{\{slemaign, rrosespi, sisbot, rachid\}@laas.fr}
	\and
	S\'everin Lemaignan \and Michael Beetz
	\at
	Intelligent Autonomous Systems, Technische Universität München, Munich, Germany\\
	\email{\{lemaigna, beetz\}@in.tum.de}
}

@@

\item \emph{Knowledge representation and management}: the robot is endowed with
an active knowledge base that provides a logically sound symbolic model of its
beliefs of the world, as well as models for each cognitive agent the robot
interacts with. Each of these models is independent and logically consistent,
enabling reasoning on different perspectives of the world that would otherwise
be considered inconsistent (for instance, an object can be visible for the
robot but not for the human. This object can have at the same time the property
\concept{isVisible \textbf{true}} and \concept{isVisible \textbf{false}} using
two different models).  Our platform relies on OWL-DL\footnote{\emph{Web
Ontology Language - Description Logics}, a decidable subset of the first-order
logics, \url{http://www.w3.org/TR/owl2-primer/}} ontologies and features
continuous storage, querying and event triggering over the pool of facts known
by the robot.

@@

Dialogue processing in real robots have been explored by several teams.  Brick
and Scheutz~\cite{Brick2007} have contributions regarding natural language
processing in an incremental way, and how this enables instant back-channel
feedback (like nodding). Hüwel et al.~\cite{Huwel2006} propose the concept of
\textit{Situated Semantic Unit}: atoms are extracted from sentences exposing
semantic links to other units. The parser tries to satisfy these links and
rates the semantic interpretation of the sentence. Used in conjunction with
ontologies, their approach offers robustness to ungrammatical or partial
utterances. They validated the approach with an extensive user-study.

Zender et al.~\cite{Zender2009} address the generation of referring expressions
(\emph{GRE}) in situated dialogue for topological knowledge.  They consider
both the reference resolution and reference description tasks, and rely on
OWL-DL representation and SPARQL\footnote{{\em SPARQL Protocol and RDF Query
Language}, \url{http://www.w3.org/TR/rdf-sparql-query/}} to extract
\emph{topological contexts} from their knowledge base.

@@

Beetz et al.~\cite{Beetz2010} proposes a cognitive architecture called
\textsc{CRAM} (Cognitive Robot Abstract Machine) that integrates
\textsc{KnowRob}~\cite{Tenorth2009a}, a knowledge processing framework based on
Prolog. Its underlying storage is based on an OWL ontology, derived from
\textsc{OpenCyc}. \textsc{CRAM} and \textsc{KownRob} have been demonstrated on
several real-world scenarios, where natural language recipes extracted from
Internet had to be translated into plans and executed in a kitchen environment,
perceived and rebuilt on-line by the robots. While Prolog offers more flexible
modeling (no constraints on the arity of predicate, where Description Logics as
used in our work are limited to binary predicates), it is based on the closed
world assumption (if something cannot be inferred to be true, it is inferred to
be false) whereas we rely on the open world assumption, which is more realistic
in real world scenarios. A probabilistic extension of \textsc{KnowRob}, called
\textsc{ProbCog}~\cite{Jain2009} is also available. While in principle
possible, currently the CRAM architecture does not provide explicit support for
interacting with humans.

@@

	\item standard SPARQL queries.

@@

\begin{figure}[!ht]
\begin{center}
\scriptsize
\begin{alltt}
>> IMPERATIVE
VP: \textbf{remember} (present simple)
    SUBSENTENCE (aim: that)
      NP: \textbf{I}
      VP: \textbf{want} (present simple)
        direct objects: 
          NP: \textbf{you}
        secondary VP: \textbf{give} ()
              direct objects:
                NP: my \emph{nice blue} \textbf{bottle}
              indirect objects:
                NP: \textbf{me}
\end{alltt}
\end{center}
\caption{Raw output of the {\sc Dialogs} parser after processing the
sentence: ``remember that I want you to give me my nice blue bottle.'' 
Nominal groups are not grounded yet.} 
\label{dialog|parser_output}
\end{figure}
